---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(dplyr)
```
# load data moviename
```{r}
moviename <- read_tsv('title.akas.tsv.gz')
```

```{r}
moviename
```

# the movie name is Avengers: Endgame
```{r}
filter(moviename,title=="Avengers: Endgame")
```

# connect to the SQLite
```{r}
mydb <- src_sqlite("/Users/zimin/Downloads/movie.db",create = F)
mydb
```

# load data
```{r}
movierate <- tbl(mydb,"rating")
movierate
```

# ratings mean is 6.885 and Median is 7.1
```{r}
summary(movierate)
```

# select Avengers: Endgame Id to find this movies averagerating is 8.4, higher than ratings mean
```{r}
filter(movierate,tconst=="tt4154796")
```

# make a plot to show how many movie's rating is higher than 8.4
```{r}
rating <- ggplot(movierate)+
             geom_bar(aes(x=averageRating,col=averageRating>=8.4))
  
rating
```

# laod table "year"
```{r}
moviebasics <- tbl(mydb,"year")
moviebasics
```


# in moviebasics dataset the tvEpisode has the most amount,and the movie is the third 
```{r}
type <- ggplot(moviebasics)+
         geom_bar(aes(x=titleType,fill=titleType),
                  show.legend = FALSE)+
        theme(aspect.ratio = 1)+
        labs(x=NULL,y=NULL)
type+coord_polar()
```

# select Avengers: Endgame from SQLite
```{r}
tbl(mydb,sql("SELECT * FROM year WHERE tconst=='tt4154796'"))
```

# Use movie ID to find the directors Id
```{r}
moviecrew <- tbl(mydb,sql("SELECT * FROM crew WHERE tconst=='tt4154796'"))
moviecrew
```

# load table moviedirectors
```{r}
moviedirectors <- tbl(mydb,"moviedirectors")
moviedirectors
```

# select directors ID
```{r}
endgamedirectors <- filter(moviedirectors,nconst%in%c('nm0751577','nm0751648'))
endgamedirectors
```

# Russo brother's movie release country
```{r}
russomovie <- filter(moviename,titleId%in%c('tt3498820','tt1843866','tt4154756','tt4154796'))
russomovie
```

# select their movies
```{r}
russobasics <- filter(moviebasics,tconst%in%c('tt3498820','tt1843866','tt4154756','tt4154796'))
russobasics
```

```{r}
rating1 <- read_tsv('title.ratings.tsv.gz')
```


```{r}
russorating <- filter(rating1,tconst%in%c('tt3498820','tt1843866','tt4154756','tt4154796'))
russorating
```

# Add new colume to russorating.budget,boxoffice(domestic&international) data from BOX Office Mojo
```{r}
attach(russorating)
russorating$moviename <- c("Captain America:The Winter Soldier","Captain America: Civil War","Avengers: Infinity War","Avengers: Endgame")
russorating$movieyear <- c("2014","2016","2018","2019")
russorating$budget <- c("170000000","250000000","316000000","356000000")
russorating$domestic <- c("259766572","408084349","678815482","858373000")
russorating$international <- c("454654931","745211944","1369544272","1939427564")
russorating
```

```{r}
russorating$domestic <- as.numeric(russorating$domestic)
russorating$international <- as.numeric(russorating$international)
```


# make a function to calculate returnmoney
```{r}
returnmoney <- function(domestic,international){
  result <- domestic*0.45+international*0.3
  print(result)
}
```

```{r}
return <- returnmoney(russorating$domestic,russorating$international)
```

# Add returnmoney to russorating
```{r}
attach(russorating)
russorating$moviename <- c("Captain America:The Winter Soldier","Captain America: Civil War","Avengers: Infinity War","Avengers: Endgame")
russorating$movieyear <- c("2014","2016","2018","2019")
russorating$budget <- c("170000000","250000000","316000000","356000000")
russorating$domestic <- c("259766572","408084349","678815482","858373000")
russorating$international <- c("454654931","745211944","1369544272","1939427564")
russorating$return <- c("253291437","407201540","716330248","968096119")
russorating
```


```{r}
russorating$return <- as.numeric(russorating$return)
russorating$budget <- as.numeric(russorating$budget)
```


# make a function to calculate investor earnings.These four films have good earnings.
```{r}
earnings <- function(return,budget){
  result <- return-budget
  print(result)
}
```

```{r}
investorearnings <- earnings(russorating$return,russorating$budget)
```

# russo brother's movie rating, These four films rating higher than rating mean(rating mean is 6.885)
```{r}
moverate <- ggplot(russorating)+
            geom_point(aes(x=moviename,y=averageRating),col="red")
moverate
```


# Movies and films with a rating higher than 7.7 account for about 35% of all, according to the Russo Brothers’ movies ratings and final earnings, the next movie will also receive a good result.
```{r}
russorating <- ggplot(movierate)+
         geom_bar(aes(x=averageRating,col=averageRating>=7.7),
                  show.legend = FALSE)+
        theme(aspect.ratio = 1)+
        labs(x=NULL,y=NULL)
russorating+coord_flip()
```

